A Methodology and Implementation of Automated Emissions Harmonization for Use in Integrated Assessment Models

### 2018-01-31 paper.tex
finished most of reviewer 3 changes

In order to show a representative cross section of the performance of the
\code{aneris} harmonization procedure, we focus on the harmonization of results
of the \gls{iam} MESSAGE-GLOBIOM \cite{fricko_marker_2017}. Two scenarios from the \gls{ssp}
scenario library \cite{Riahi2017153,Rao2017346} are presented. The SSP2, or
``middle of the road'', scenario (referred to as SSP2-Ref) is chosen to be
analyzed because MESSAGE-GLOBIOM is the marker scenario for this \gls{ssp}. This SSP2
scenario lies between two \glspl{rcp}, 6 and 8.5, with a radiative forcing level of
approximately 6.5 Wm$^{-2}$. We additionally present the results for the
SSP2-based mitigation scenario leading to a radiative forcing of 4.5 Wm$^{-2}$
(referred to as SSP2-4.5). The SSP2-45 scenario is chosen because mitigation
technologies and policies are enacted causing a general reduction in pollutants
and \glspl{ghg}, including (eventual) negative \cotwo emissions in some regions and
sectors due to carbon capture and sequestration and afforestation. A scenario in
which negative emissions play a role in mitigation strategies is particularly
important because of the sensitivity of key indicators, such as end-of-century
radiative forcing (which is used to estimate mean global temperature increase),
to the timing and magnitude of net-zero and total negative \cotwo
emissions. Therefore, these two scenarios represent two relative extreme cases
in the use of a harmonization approach and thus provide a case study as to its
general applicability. Figure \ref{fig:kyoto} shows the different trends of
Kyoto Gases in each scenarios.

@@

We investigate the aggregate effect of harmonization with all necessary override
methods on total anthropogenic radiative forcing projections with the simple
carbon-cycle and climate model, MAGICC6 \cite{meinshausen2011emulating,
  meinshausen2011rcp}, for each harmonized and unharmonized scenario
respectively as shown in Figure \ref{fig:forcing}. We find that the change due
to harmonization is small, ranging between 1 and 2.5\% over the model
horizon. Relative near-term differences persist in the mitigation case (SSP-4.5)
because differences in near-term emissions define to a larger degree the
longer-term forcing outcome due to the cumulative nature of long-lived climate
forcers like \cotwo.  The resulting difference in forcing in 2100 is 0.04
$\frac{\text{W}}{\text{m}^2}$ for SSP2-4.5 and 0.01
$\frac{\text{W}}{\text{m}^2}$ for SSP2-Ref, both of which are well within
acceptable tolerances (e.g., 0.75 $\frac{\text{W}}{\text{m}^2}$ defined for
\gls{smip} \cite{oneill_scenario_2016}). Thus harmonization is considered to
have a negligible effect on key long-term climate indicators.

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{results_forcing.pdf}
    \caption[]{
      \label{fig:forcing}
      The results of the simple climate model, MAGICC6, forced with the SSP2-Ref
      (blue) and SSP2-4.5 (green) harmonized and unharmonized scenarios is
      presented. The radiative forcing trajectories of harmonized and
      unharmonized scenarios are shown in solid lines and dashed lines,
      respectively.  }
  \end{center}
\end{figure}
\section{Discussion \& Future Work}\label{sec:future}

This work presented a novel methodology and Python implementation of automated
emissions harmonization for \glspl{iam}, \code{aneris}. An in-depth explanation of the
processes and methods for determining the use of harmonization methods was
provided in Section \ref{sec:meths}. \code{aneris} was able to satisfactorily
harmonized over 96\% of the 1940 individual trajectories that were analyzed in
Section \ref{sec:results}. Of the remaining trajectories, harmonization method
overrides were applied, and example situations in overrides were needed were
discussed.

>>>>

In order to show a representative cross section of the performance of the
\code{aneris} harmonization procedure, we focus on the harmonization of results
of the \gls{iam} MESSAGE-GLOBIOM \cite{fricko_marker_2017}. Two scenarios from
the \gls{ssp} scenario library\footnote{We refer the reader to the broad
  literature discussing the SSPs, e.g.,
  \cite{vuuren_new_2013,oneill_scenario_2016, oneill_new_2013} for a more in
  depth discussion of the scenario architecture and design.} are presented. The
SSP2 \cite{Riahi2017153,Rao2017346}, or ``middle of the road'', scenario
(referred to as SSP2-Ref) is chosen to be analyzed because MESSAGE-GLOBIOM is
the marker scenario\footnote{The concept of ``marker'' scenarios are used to
  illustrate distinctive scenario types within the SSP scenario framework. See
  \cite{vuuren_new_2013} and \cite{Riahi2017153} for a more lengthy
  description.} for this \gls{ssp}. This SSP2 scenario lies between two
\glspl{rcp}, 6 and 8.5, with a radiative forcing\footnote{Radiative forcing is a
  measurement of the capacity for different emissions species to affect
  tropopausal irradiance and has a relationship to global mean equilibrium
  temperature change. We refer the reader to \cite{IPCCWG1PhysicalStocker2013}
  for a more detailed discussion.} level of approximately 6.5 Wm$^{-2}$. We
additionally present the results for the SSP2-based mitigation scenario leading
to a radiative forcing of 4.5 Wm$^{-2}$ (referred to as SSP2-4.5). The SSP2-45
scenario is chosen because mitigation technologies and policies are enacted
causing a general reduction in pollutants and \glspl{ghg}, including (eventual)
negative \cotwo emissions in some regions and sectors due to carbon capture and
sequestration and afforestation. A scenario in which negative emissions play a
role in mitigation strategies is particularly important because of the
sensitivity of key indicators, such as end-of-century radiative forcing (which
is used to estimate mean global temperature increase), to the timing and
magnitude of net-zero and total negative \cotwo emissions. Therefore, these two
scenarios represent two relative extreme cases in the use of a harmonization
approach and thus provide a case study as to its general applicability. Figure
\ref{fig:kyoto} shows the different trends of Kyoto Gases in each scenarios.

@@

We investigate the aggregate effect of harmonization with all necessary override
methods on total anthropogenic radiative forcing projections with the simple
carbon-cycle and climate model, MAGICC\footnote{MAGICC is a reduced complexity
  climate model which incorporates future trajectories of forcing agents (i.e.,
  emissions) to estimate future radiative forcing and mean global temperature
  response. We refer the reader to the
  \href{http://wiki.magicc.org/index.php?title=Model_Description}{MAGICC wiki}
  for a more in-depth description.} \cite{meinshausen2011emulating,
  meinshausen2011rcp}, for each harmonized and unharmonized scenario
respectively as shown in Figure \ref{fig:forcing}. We find that the change due
to harmonization is small, ranging between 1 and 2.5\% over the modeled time
period. Relative near-term differences persist in the mitigation case (SSP-4.5)
because differences in near-term emissions define to a larger degree the
longer-term forcing outcome due to the cumulative nature of long-lived climate
forcers like \cotwo.  The resulting difference in forcing in 2100 is 0.04
$\frac{\text{W}}{\text{m}^2}$ for SSP2-4.5 and 0.01
$\frac{\text{W}}{\text{m}^2}$ for SSP2-Ref, both of which are well within
acceptable tolerances (e.g., 0.75 $\frac{\text{W}}{\text{m}^2}$ defined for
\gls{smip} \cite{oneill_scenario_2016}). Thus harmonization is considered to
have a negligible effect on key long-term climate indicators.

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{results_forcing.pdf}
    \caption[]{
      \label{fig:forcing}
      The results of the simple climate model, MAGICC6, forced with the SSP2-Ref
      (blue) and SSP2-4.5 (green) harmonized and unharmonized scenarios is
      presented. The radiative forcing trajectories of harmonized and
      unharmonized scenarios are shown in solid lines and dashed lines,
      respectively.  }
  \end{center}
\end{figure}

\section{Discussion \& Future Work}\label{sec:future}

This work presented a novel methodology and Python implementation of automated
emissions harmonization for \glspl{iam}, \code{aneris}. An in-depth explanation
of the processes and methods for determining the use of harmonization methods
was provided in Section \ref{sec:meths}. \code{aneris} was able to
satisfactorily harmonized over 96\% of the 1940 individual trajectories that
were analyzed in Section \ref{sec:results}. Of the remaining trajectories,
harmonization method overrides were applied, and a discussion was provided
detailing why overrides were deemed necessary.
